---
title: "DATA607_ASSIGNment_3"
author: "Vincent Colardi"
date: "September 15, 2018"
output: html_document
---

## 3. Copy the introductory example. The vector name stores the extracted names.

```{r}
raw.data <-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"
raw.data
library(stringr)
```

#### 1. Use the tools of this chapter to rearrange the vector so that all elements conform to the standard first_name last_name
```{r}
names <- unlist(str_extract_all(raw.data,"[[:alpha:]]{2,}"))
names <- unlist(str_replace_all(names, "Dr", " "))
names <- unlist(str_replace_all(names, "Rev", " "))
names <- unlist(str_replace(names,"Simpson", "temporary"))
names <- unlist(str_replace(names,"Homer", "Simpson"))
names <- unlist(str_replace(names,"temporary", "Homer"))
names <- unlist(str_replace(names,"Montgomery", "temporary"))
names <- unlist(str_replace(names,"Burns", "Montgomery"))
names <- unlist(str_replace(names,"temporary", "Burns"))
names <- unlist(str_extract_all(names,"[[:alpha:]]{2,}"))
names
```

#### 2. Construct a logical vector indicating whether a character has a title (i.e., Rev. and Dr.).
```{r}
title <- unlist(str_extract_all(raw.data,"[[:alpha:]]{2,}"))
tosearch <- c("Rev","Dr")
str_detect(title,tosearch)
```

#### 3. Construct a logical vector indicating whether a character has a second name
```{r}
second_name <- unlist(str_extract_all(raw.data,"[[:alpha:].,]{2,}"))
replace_str <- c("Dr.", "Rev.")
second_name <- str_replace_all(second_name, replace_str,"")
second_name
str_detect(second_name,"\\.")
```


## 4. Describe the types of strings that conform to the regular expressions and construct an example that is matched by the regular expression.

#### 1. [0-9]+\\$
#### The regular expression will match the first occurence of a digit from 1->9 followed by a special character $
```{r}
example_str <- "1$sample text 2$sample text"
unlist(str_extract(example_str, "[0-9]+\\$"))
```

#### 2. \\b[a-z]{1,4}\\b
#### The regular expression extracts out words of size 1 to 4 from the vector which are on a word edge before and after the word match
```{r}
shopping_list <- c("apples x4", "bag of flour", "bag of sugar", "milk x2")
str_extract_all(shopping_list, "\\b[a-z]{1,4}\\b")
```
#### 3. .*?\\.txt$
#### The regular expression is looking for the pattern of any word followed by a ".txt" string; the prceding word is optional
```{r}
sample_str <- c("test.txt","test",".txt")
str_extract_all(sample_str, ".*?\\.txt$")
```
#### 4. \\d{2}/\\d{2}/\\d{4}
#### This regular expression appears to search for a date format consisting of dd/dd/dddd 
```{r}
digit_str <- c("12/22/1962",2345, "10/25", "/1982")
str_extract_all(digit_str, "\\d{2}/\\d{2}/\\d{4}")
```
#### 5. <(.+?).+?</\\1>
#### This regular expression searches for a pattern of "<" followed by any number of chars and "</" followed by 1 character which matches the first char of the first string
```{r}
test_str <- c("<tee </t","<t <r")
str_extract_all(test_str, "<(.+?).+?</\\1") 
```

